---
title: "Exercise 3"
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
author: "Valentin Mesmer (12578200), Tim-Luis Hartenfels (12597574), Junis Al Attar (12574322)"
date: "`r Sys.Date()`"
output: pdf_document
---


## Exercise 1: Initializing git (4 Points)

d) Strengths of Git:

    1. Git enables every developer working on a project to have a copy of the repository at a special version, so he can work offline and synchronize with the repository when connected to the internet
    
    2. Developers can create branches to work on different features or versions and merge them later.
    

    Weaknesses of Git:

      1. It may be hard to learn git, because at the beginning learners may have some problems to create an account and to understand the connection between e.g. GitHub and their local version.
    
      2. Git tracks the changes in files line by line, which is really great for code, but really bad for large files like images, zips or binaries.
      
      
## Exercise 2: Putting your Repository on GitHub (3.5 Points)

a) [GitHub Repository](https://github.com/jualat/exeRcise-sheet-3)


## Exercise 3: Baby-Names in Munich (4.5 Points)

b)
    ```{r}
    library(readr)

    data2022 <- read_csv("vornamen_2022.csv",col_types = 
                           cols(Vorname = col_character(), 
                                Anzahl = col_character(), 
                                Geschlecht = col_character()))
    data2021 <- read_csv("vornamen_2021.csv",col_types = 
                            cols(Vorname = col_character(), 
                                 Anzahl = col_character(), 
                                 Geschlecht = col_character()))
    ```
    
    Type of "Anzahl": Character
    
    Its not numeric, because there are rows called "4 oder weniger", which is not numeric
    
    
    ```{r, warning=FALSE, message=FALSE}
    library(readr)
    library(dplyr)
    
    data2022 <- data2022 %>% 
    mutate(Anzahl = ifelse(Anzahl == "4 oder weniger", 2.5, as.numeric(Anzahl)))

    data2021 <- data2021 %>% 
    mutate(Anzahl = ifelse(Anzahl == "4 oder weniger", 2.5, as.numeric(Anzahl)))

    ```  
    
    
    We set all "4 oder weniger" to 2.5, because this is the mid of the possible values 1,2,3,4. 
    
    On top of this its not a natural number, so it's obvious that it's not a real measured value.
    

c)

    ```{r}
    total_babies_2022 <- sum(data2022$Anzahl, na.rm = TRUE)
    total_babies_2021 <- sum(data2021$Anzahl, na.rm = TRUE)
    
    if (total_babies_2022 > total_babies_2021) {
      bigger_baby_boom_year <- 2022
    } else if (total_babies_2022 < total_babies_2021) {
      bigger_baby_boom_year <- 2021
    } else {
      bigger_baby_boom_year <- NULL
    }
    
    
    if (is.null(bigger_baby_boom_year)) {
      cat("There was no significant difference in baby booms between 2021 and 2022.")
    } else {
      cat("The year with the bigger baby boom is", bigger_baby_boom_year)
    }
  
    ```
 
   
d)

    ```{r}
    data2022 <- data2022 %>%
    mutate(year = 2022)

    data2021 <- data2021 %>%
    mutate(year = 2021)
    ```

e)

    ```{r}
    combined_data <- bind_rows(data2022, data2021)
    ```

f)

    ```{r}
    library(knitr)
    top_names <- combined_data %>%
    group_by(Vorname) %>%
    summarize(count = sum(Anzahl, na.rm = TRUE)) %>%
    arrange(desc(count)) %>%
    head(10)
    kable(top_names, caption = "Top 10 Most Popular Names")
    ```


    

## Exercise 4: Chat GPT + apply (3 points)

a)


  
    ```{r}
    tax_data <- data.frame( Name = c("Munich GmbH", "ABC Inc.", 
                                     "Backpacks 1980", "Bavarian Circus"),
    Tax_2019 = c(5000, 4000, 6000, 3500), 
    Tax_2020 = c(4800, 4200, 5800, 3700), 
    Tax_2021 = c(5200, 3800,5900, 3400))
    ``` 

    The incorrect apply function used in the code is lapply(tax_data[, -1], 2, mean). The correct apply function to calculate column-wise means is sapply.
    
    
    ```{r}
    column_means <- sapply(tax_data[, -1], mean)
    ``` 
    
    
    To calculate the row-wise means, you can use the rowMeans function.
    
    ```{r}
    row_means <- rowMeans(tax_data[, -1])
    ``` 
    
    
    This code will calculate the means of each row in the tax_data data frame, excluding the first column. The resulting row_means object will be a vector containing the means of each row.
    
    
